Macroscopic Salt Rejection through Electrostatically Gated Porous Graphene

### 2018-10-25 paper/paper.tex
Change pore density

%%%%%%%%%%%%%%%%%%%%
%Main
%%%%%%%%%%%%%%%%%%%%
\begin{document}
\clearpage{}
\begin{abstract}
  {\normalsize Atomically thin graphene nanopores is emerging as one
    of the most promising candidates for next-generation membrane
    technology owing to the ultrahigh permeability. However, the
    size-exclusive mechanism of selectivity limits its scalability as
    it remains technically challenging to drill subnanometer pores
    over a large area. Here we report macroscopic salt rejection
    through atomically-thin porous graphene with the pore sizes of
    20$\pm$10 nanometers, and a pore density of 1.25$\times$10$^{10}$
    cm$^{-2}$, overcoming the pore size limitation set by the hydrated
    radii. By electrostatically gating a sheet of porous graphene, we
    report a considerable reduction of salt flux by up to 55\% and
    85\% with the gate voltage, based on our experiments and
    theoretical predictions, respectively. We systematically
    investigate the effects of salt concentration and species,
    including developing a theory to model the electrolyte diffusion
    through a nanopore in a sheet of gated graphene. The interplay
    between graphene quantum capacitance and electrical double layer
    is identified to be the main mechanism responsible for the
    observed salt rejection, when the pore size is comparable to the
    Debye length. Our findings reveal a new degree of
    freedom controlling the membrane potential and electrolyte
    permeation through porous two-dimensional materials.  }
\end{abstract}

@@

\Fig{} \ref{fig:1}a depicts the experimental setup characterizing
ionic diffusion through a sheet of double layer porous graphene
(PG). Two reservoirs, namely the high-concentration reservoir (HCR)
containing electrolyte solution with molar concentration $c_0$, and
the low-concentration reservoir (LCR) containing de-ionized (DI)
water, are separated by a PG membrane supported by polycarbonate
track-etched (PCTE) film. Magnetic stirrers are used to minimize the
effects of external concentration polarization, and a conductivity
probe is placed in the LCR to monitor the ionic concentration as a
function of time. The membrane is attached to a piece of copper tape
connected to a voltage source applying an electrical bias
$V_{\mathrm{G}}$, with the LCR grounded (\Fig{} \ref{fig:1}a
inset). We fabricated the PCTE-supported PG using the protocol
developed by our group \cite{Choi_2018}, as schematically shown in
\Fig{} \ref{fig:1}b. The normally distributed, circular pores with
pore diameters of 20$\pm$10 nm (\Fig{} \ref{fig:1}c inset) over a
large area were perforated on graphene.  By optimizing the subsequent
transfer process, a high surface coverage ($>$ 98\%) of PG on PCTE was
obtained (\Fig{} \ref{fig:1}c), allowing reliable characterization of
the ion transport behavior (details see Supplementary Information
Section S1).  The system presented here allows us to systematically
investigate the diffusive flux of ions across a sheet of PG,
$\boldsymbol{J}$, driven by the gradient of electrochemical potential
in the electrolyte medium.

>>>>

%%%%%%%%%%%%%%%%%%%%
%Main
%%%%%%%%%%%%%%%%%%%%
\begin{document}
\clearpage{}
\begin{abstract}
  {\normalsize Atomically thin graphene nanopores is emerging as one
    of the most promising candidates for next-generation membrane
    technology owing to the ultrahigh permeability. However, the
    size-exclusive mechanism of selectivity limits its scalability as
    it remains technically challenging to drill subnanometer pores
    over a large area. Here we report macroscopic salt rejection
    through atomically-thin porous graphene with the pore sizes of
    20$\pm$10 nanometers, and a pore density of 1.25$\pm$0.25$\times$10$^{10}$
    cm$^{-2}$, overcoming the pore size limitation set by the hydrated
    radii. By electrostatically gating a sheet of porous graphene, we
    report a considerable reduction of salt flux by up to 55\% and
    85\% with the gate voltage, based on our experiments and
    theoretical predictions, respectively. We systematically
    investigate the effects of salt concentration and species,
    including developing a theory to model the electrolyte diffusion
    through a nanopore in a sheet of gated graphene. The interplay
    between graphene quantum capacitance and electrical double layer
    is identified to be the main mechanism responsible for the
    observed salt rejection, when the pore size is comparable to the
    Debye length. Our findings reveal a new degree of
    freedom controlling the membrane potential and electrolyte
    permeation through porous two-dimensional materials.  }
\end{abstract}

@@

\Fig{} \ref{fig:1}a depicts the experimental setup characterizing
ionic diffusion through a sheet of double layer porous graphene
(PG). Two reservoirs, namely the high-concentration reservoir (HCR)
containing electrolyte solution with molar concentration $c_0$, and
the low-concentration reservoir (LCR) containing de-ionized (DI)
water, are separated by a PG membrane supported by polycarbonate
track-etched (PCTE) film. Magnetic stirrers are used to minimize the
effects of external concentration polarization, and a conductivity
probe is placed in the LCR to monitor the ionic concentration as a
function of time. The membrane is attached to a piece of copper tape
connected to a voltage source applying an electrical bias
$V_{\mathrm{G}}$, with the LCR grounded (\Fig{} \ref{fig:1}a
inset). We fabricated the PCTE-supported PG using the protocol
developed by our group \cite{Choi_2018}, as schematically shown in
\Fig{} \ref{fig:1}b. The normally distributed, circular pores with
pore diameters of 20$\pm$10 nm and a pore density of
1.25$\pm$0.25$\times$10$^{10}$ cm$^{-2}$ (\Fig{} \ref{fig:1}c inset) over a
large area were perforated on graphene.  By optimizing the subsequent
transfer process, a high surface coverage ($>$ 98\%) of PG on PCTE was
obtained (\Fig{} \ref{fig:1}c), allowing reliable characterization of
the ion transport behavior (details see Supplementary Information
Section S1).  The system presented here allows us to systematically
investigate the diffusive flux of ions across a sheet of PG,
$\boldsymbol{J}$, driven by the gradient of electrochemical potential
in the electrolyte medium.
